A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2016-11-08 manuscript_3.tex
more review, mostly verb tenses and such

All networks are initialized equally. The number of nodes for every network is 4122, the same as in the FOSISS network.
To every agent the same utility is given and to every edge the same trust weight is assigned. In the case of FOSISS
network, trust is given by the number of collaborations among researchers, utility remains the same for all nodes as in
the other networks.\\

@@

{\color{red} For the agent to decide to whether cooperate or not, $\eta$ is
  compared to a global threshold $\nu$. If the agents' $\eta$ $>$ $\nu$,
  then the agent will cooperate, otherwise will act suspiciously and it will
  defect. $\nu$ is a global parameter that establishes a threshold that an
  agents' $\eta$ must cross in order to decide to cooperate. In such a way,
  $\eta$ can limit the size of the population of cooperators. Due
  to what the system and the game can offer to agents in terms of utilities and the strength
  of collaboration relationships, $\eta$ represents the carrying capacity of the
  system for the population of cooperators}.

@@

We ran two different experiments. In the first we simulated different values of
carrying capacity $\nu$. With this experiment we were able to see how number of
cooperators, utility, strength of connections among agents and the ratio of
shifting state population would change in the range of the carrying
capacity. For this experiment the states of the agents were the same at
initialization, for all values of the carrying capacity. Since the model is
deterministic, it will return the same result if ran under the same
conditions.\\

The second experiment consisted in running the simulation under the same degree of carrying capacity $\nu$ but randomizing the initial states of the agents. This would show if the system converges to a global state. For every network, the simulation was run 100 times and results were averaged.

@@

Watts-Strogatz networks \cite{Watts1998} (small-world networks) are in a regime between a fully regular grid (lattice) and a random network (Erd\"{o}s-R\'enyi). In order to build them, a node is chosen from a lattice (a ring) and the edge that connects it to nearest neighbor in a clockwise sense. With probability $p$, this edge is reconnected to a node chosen uniformly at random over the entire ring, with duplicate edges forbidden; otherwise the edge is left in place. This process is repeated by moving clockwise around the ring, considering each node in turn until one lap is completed. Next, the edges connect nodes to their second-nearest neighbors clockwise. And as before, randomly rewire each of these edges with probability $p$, and continue this process, circulating around the ring and proceeding outward to more distant neighbors after each lap, until, each edge in the original lattice has been considered once. The main characteristic of these networks is that the average shortest path length is small and grows as $log(N)$ ($\langle l \rangle \sim log(N)$). Also, the average clustering coefficient $\langle C \rangle$ remains large in terms of $p$. For $p < 0.1$, $\langle C \rangle \sim 1$.

@@

The biomedical research network on which we are running our model was generated 
with data from collaborative projects. Our data was obtained from CONACyT and includes information for twelve years of \textit{FOSISS} grants. Data included names of Principal Investigators, collaborators, research topics, etc. The network we are using here has researchers as nodes and edges represent the connection of two scientists when they participate in the same project. Edges are also weighted according to the number of projects shared by any pair of scientists.\\

@@

In the case of the Watts-Strogatz, small-world network, the whole population
remains cooperating for ranges between $0$ and $0.2$ but as it gets closer to
$0.2$, more time is needed for the population to become full of cooperators. In
$\nu \approx 0.2$ the cooperators will represent only half of the population and
such number of them will be constant up to $\nu \approx 0.25$ forming a short
plateau. From $\nu \approx 0.25$ to $\nu \approx 0.6$ cooperators will be
present at the beginning of the simulation but will go diminishing as time passes
by. In the case of the Barab\'asi-Albert network, crossing the threshold of $\nu
\approx 0.2$, there is a sharp decrease in the number of cooperators, but stays
constant over time. Such behavior is present for a very short range of $\nu$, and
before $\nu \approx 0.24$, cooperators disappear for the rest of values of
$\nu$. Finally, FOSISS network behaves similar to the other networks in that
there is a fall in the number of cooperators close  $\nu \approx 0.2$. Different
to the other networks, FOSISS network lacks the sharp reduction of
cooperators, instead this population declines smoothly and progressively;
specially, when it reaches a $\nu \approx 0.25$ cooperators go 
decreasing in a less dramatic manner all the way to $\nu \approx 0.5$. It is
also worth of mention that from $\nu = 0$ to $\nu \approx 0.5$ the number of
cooperators converge to a certain amount and stays constant for the rest of the
simulation.

@@

The distribution of utility on each topology is induced by the degree
distribution. This is so, since a given agent (node) will interact with its
neighbors to either cooperate or defect, in such a way that connectivity
influences the number of events played and thus the likelihood of increasing its
corresponding utility. For instance, utility distribution in the random,
Erd\"{o}s-R\'enyi network displays a normal-like curve. The algorithm that
generates this kind of topology, assigns to every node the same probability of
connecting with any other node, which produces a \textit{poissonian} degree
distribution \cite{Erdos1959}. Since the Watts-Strogatz degree distribution is
described by a function that is midways between a random distribution and a
scale-free network \cite{Barrat2000} one may expect also  an intermediate
behavior of the utility distribution, assumption that seems to be fulfilled by
the distribution in Figure 6B.

@@

The Barab\'asi-Albert network (7C) presents also a symmetric unimodal
distribution with values higher (on average) than those of the Erd\"{o}s-R\'enyi
random network, this may be the effect of increased communication due to more
efficient network navigability. Interestingly, the network corresponding to the
real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
moderate to high values of strength of interactions are more likely. We can
hypothesize that this effect is also due to the communication properties of the
network.

@@

An interesting feature of highly communicated networks (characterized by high values of clustering coefficient) is the
fact that certainty among players seem to be enhanced, that is, in such networks the rate of change of strategy is
significantly lower (and smoother) than in poorly connected networks. This is another instance in which easier
communication (i.e. lower average minimum path lengths) lead to better performance of the whole collaborative research
system.\\

@@

{\color{red}Under the assumptions given by the model, we were able to notice
  that, in general, communication within the social
collaborative networks has a positive correlation with average strength of interactions between the individuals partaking in the games and
also with the global collective utility (given by the sum of the individual payoffs). The better the
communication among players, the higher the strength of interactions and the utility leading to an optimized functioning of the whole
\emph{scientific collaboration system}. This is an important result that may be useful for scientific policy planning
and may set a foundation for the optimal use of social networks in scientific collaboration as a means to improve the
relationships among collaborating peers and thus ultimately the performance of research systems. It is out of question
the fact that we need more qualitative work in order to validate these results from a sociological and anthropological
perspective.\\ %Furthermore, such validation is necessary because, as we said at
             %the beginning of this work, \emph{strength of interactions} can
             %have many different meanings and implementations in the real
             %world. The same we can say about \emph{utility} and most of all,
             %about the very idea of the game we explored here since ``playing
             %the game'' must have so, many different meanings among resarchers
             %and their communities.}\\

{\color{red}In order to close this article, we would like to comment on three issues we consider important. The first one is about
confronting our results with our available data of the biomedical research community. Second, we believe is important
saying something about the role of computational simulations in the social sciences. One last point would be about our
future work.}\\

@@

{\color{red}FOSISS network is higly hierarchical according to its heterogeneity of $0.873$. Because of it, one would
  expect to find the presence of important hubs \cite{Wu-etal2008}, that is, some few researchers that control the whole
  network as it has been reported in some other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
  centralization is very low $0.023$, that is, there are no researchers that centralize the majority of connections. Our
  guess is that the network is composed of many small communities or groups with a central researcher or Principal
  Investigator (PI). If this is FOSISS network scenario, it means that those groups have a very hierarchic structure as well.}\\

{\color{red}Under such structure, when the clustering coefficient is considered, it can be said that groups are also well connected
but that inter-groups connections are sparse. In other words, individual groups are strongly connected but the network
as a whole is supported by a small number of links. This idea is partially by
another study about scientific collaborations based on co-authorships in one of
the research centers that is part 
of the FOSISS network \cite{HernandezLemus2013}. In the cited reference an apparently well integrated community was
found (high clustering coefficient and a very short characteristic path length). Such integration was no more than
superficial, since it depended on the presence of external collaborators from other research institutions (most of them from overseas) that when removed,
the network broke into small subgraphs that worked independently. Remarkably those subgraphs corresponded to the real
groups of that research center.  What is more, several groups had a hierarchical structure as 
the one we suspect is common in FOSISS subgraphs. The results showed that collaboration was poor between groups but strong
among the members of each group, and that collaboration among groups doesn't emerge bottom-up, instead it seems to be promoted from the
top, from the administrative authorities.}\\

{\color{red}We believe that the the situation just refered is also true for the whole biomedical research community in M\'exico. The
amount of PIs who have also been collaborators in other projects is about one fifth of the total number of participants.
This is a number big enough to connect the whole network in one giant component. Yet, due to the topological
characteristics of FOSISS network, it appears to be the case in which researchers can be the leaders in one project and
collaborators of different project of \emph{its own research group}. CONACyT's funding policies makes impossible for a
researcher to get a grant from a fund if that researcher has an ongoing project with a grant from that same fund. That
is, a researcher can ask for a grant from FOSISS if and only if at the moment
doesn't have a grant from FOSISS already. This
policy has lead researchers from the same group to compete for grants from the same fund in order to rise their
budgets. As consequence of this behavior, group interactions get reinforced while is not necessarily true for integroups
connections.}\\

{\color{red}As is common among scientific communities in biomedical research, PIs play a central role in the network. Strong PIs and
well connected groups seem to be somehow responsible for the high levels of strength of interactions and the centralization of utility in
our simulation. As for what seems to be phase transitions, in the case of FOSISS networks, these are smoother than
those in the other networks with different topologies, even for those with a small-world topology. We think that this
behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first loss in the
edges that link diffrent goups and then in the edges that connect members of the groups. Connections between groups would not
be as dense as those inside the groups, which means that there would not be enough information of the behavior of one group regarding
its neighbors to constrain them as it seems to happen with individual researchers inside their communities. Nevertheless,
if values of the carrying capacity $\nu$ keep increasing and becomes more
difficult to strength of interactions, then strength of interactions begins to diminish inside groups.}\\

{\color{red}Another issue that we would like to mention about FOSISS network topology is that it is not a robust collaboration network.
At the level of groups, these might be well connected and consolidated but at the level of the network, this could be
no more than an aggregate of individual groups. A robust network would be resistant to changes in the connections
between groups but in the case of FOSISS, it seems that the network would brake down into
small research groups by cutting some edges, as it happened in our co-authorship
collaboration network \cite{HernandezLemus2013}. The lack of robustness might be 
indicative of the fact that resources stay inside the groups, that is, they do not circulate through or articulate different communities. For
example, one may think of certain expensive technologies for genomic research that could be bought once and shared
among research groups, nevertheless, this is something that doesn't seem to happen very often. There are some other
consequences, such as low communication among groups, atomization of practices and know-hows, redundancy in equipment,
difficulties for implementing community-wide infrastructures such as biobanks, etc.}\\

@@

{\color{red}On these grounds, part of our future work is based on some of the results presented here. We would like to
identify researchers in our simulations and corroborate their situation in the model and in the real world. We are
also interested in going back to the field and interview those groups with an interesting behavior found in our
simulations, probably we would follow a similar strategy as the one developed in \cite{Haraetal2003}. Finding
communities beyond the level of the groups is an important task. We think that there are many possibilities that emerge
from the integration of different methodologies. Moreover, studying social processes in science is particularly
attractive due to the amounts of data already available that can be easily collected. This is a privilege because
simulations can be designed on real world data, something that only very recently has become possible
\cite{Barabasi2011}.\\

No doubt, social sciences are getting more ``computational''. This can be seen everywhere, but curiously enough,
disciplines like physicis and computer science are the ones who are moving towards the social sciences and not so much
the other way around. It might be the case that the pioneering disciplines in the computational social sciences will set
the agenda, an agenda that will apparently be mostly based on exploiting big data and on hypothesis-free approaches. We
believe that the social science have important questions that should be added to that agenda and those questions may not
be answered only by big data techniques but they may require creating models and simulations in the style of the best
hypothesis-driven research.}

@@

\section{acknowledgements}
The authors gratefully acknowledge support by grants: CB-222220-R/2013 and
CB-179431/2012 (Consejo Nacional de Ciencia y Tecnolog\'ia). We would also like
to acknowledge CONACyT for letting us access their database. Finally, we
acknowledge the help of Francisco Allende for his work cleaning researchers
databases.

>>>>

All networks are initialized equally. The number of nodes for every network is 4122, the same as in the FOSISS network.
The same utility is given to every agent and all edges are asigned the same weight. In the case of the FOSISS
network, edge weight is given by the number of collaborations among researchers, utility remains the same for all nodes as in
the other networks.\\

@@

{\color{red} For the agent to decide whether to cooperate or not, $\eta$ is
  compared to a global threshold $\nu$. If the agents' $\eta$ $>$ $\nu$,
  then the agent will cooperate, otherwise he will be suspicious and will
  defect. $\nu$ is a global parameter that establishes a threshold that an
  agents' $\eta$ must cross in order to decide to cooperate. In this way,
  $\eta$ can limit the size of the population of cooperators. Due
  to what the system and the game can offer to agents in terms of utilities and the strength
  of collaboration relationships, $\eta$ represents the carrying capacity of the
  system for the population of cooperators}.

@@

We ran two different experiments. In the first we simulated different values of
carrying capacity $\nu$. With this experiment we were able to see how the number of
cooperators, utility, strength of connections among agents and the ratio of
shifting state population would change in the range of the carrying
capacity. For this experiment the states of the agents were the same at
initialization, for all values of the carrying capacity. Since the model is
deterministic, it will return the same result if run under the same
conditions.\\

The second experiment consisted in running the simulation under the same degree of carrying capacity $\nu$ but randomizing the initial states of the agents. This would show that the system converges to a global state. For every network, the simulation was run 100 times and results were averaged.

@@

Watts-Strogatz networks \cite{Watts1998} (small-world networks) are in a regime between a fully regular grid (lattice) and a random network (Erd\"{o}s-R\'enyi). In order to build them, a node is chosen from a lattice (a ring) and the edge that connects it to nearest neighbor in a clockwise sense. With probability $p$, this edge is reconnected to a node chosen uniformly at random over the entire ring, with duplicate edges forbidden; otherwise the edge is left in place. This process is repeated by moving clockwise around the ring, considering each node in turn until one lap is completed. Next, the edges connect nodes to their second-nearest neighbors clockwise. And as before, each of these edges is randomly rewired with probability $p$, and continue this process, circulating around the ring and proceeding outward to more distant neighbors after each lap, until, each edge in the original lattice has been considered once. The main characteristic of these networks is that the average shortest path length is small and grows as $log(N)$ ($\langle l \rangle \sim log(N)$). Also, the average clustering coefficient $\langle C \rangle$ remains large in terms of $p$. For $p < 0.1$, $\langle C \rangle \sim 1$.

@@

The biomedical research network on which we are running our model was generated 
with data from collaborative projects. Our data was obtained from CONACyT and includes information for twelve years of \textit{FOSISS} grants. Data included names of Principal Investigators, collaborators, research topics, etc. The network we are using here has researchers as nodes and edges represent the connection of two scientists when they colaborate in the same project. Edges are also weighted according to the number of projects shared by any pair of scientists.\\

@@

In the case of the Watts-Strogatz, small-world network, the whole population
remains cooperating for ranges between $0$ and $0.2$ but as it gets closer to
$0.2$, more time is needed for the population to become full of cooperators. In
$\nu \approx 0.2$ the cooperators will represent only half of the population and
such number of them will be constant up to $\nu \approx 0.25$ forming a short
plateau. From $\nu \approx 0.25$ to $\nu \approx 0.6$ cooperators will be
present at the beginning of the simulation but will go diminishing as time goes on.
In the case of the Barab\'asi-Albert network, crossing the threshold of $\nu
\approx 0.2$, there is a sharp decrease in the number of cooperators, but stays
constant over time. Such behavior is present for a very short range of $\nu$, and
before $\nu \approx 0.24$, cooperators disappear for the rest of values of
$\nu$. Finally, FOSISS network behaves similar to the other networks in that
there is a fall in the number of cooperators close  $\nu \approx 0.2$. Different
to the other networks, FOSISS network lacks the sharp reduction of
cooperators, instead this population declines smoothly and progressively;
specially, when it reaches a $\nu \approx 0.25$ cooperators go 
decreasing in a less dramatic manner all the way to $\nu \approx 0.5$. It is
also noteworthy that from $\nu = 0$ to $\nu \approx 0.5$ the number of
cooperators converge to a certain amount and stays constant for the rest of the
simulation.

@@

The distribution of utility on each topology is induced by the degree
distribution. This is so, since a given agent (node) will interact with its
neighbors to either cooperate or defect, in such a way that connectivity
influences the number of events played and thus the likelihood of increasing its
corresponding utility. For instance, utility distribution in the random,
Erd\"{o}s-R\'enyi network displays a normal-like curve. The algorithm that
generates this kind of topology, assigns to every node the same probability of
connecting with any other node, which produces a \textit{poissonian} degree
distribution \cite{Erdos1959}. Since the Watts-Strogatz degree distribution is
described by a function that is midways between a random distribution and a
scale-free network \cite{Barrat2000} one may expect also  an intermediate
behavior of the utility distribution. This assumption seems to be fulfilled by
the distribution in Figure 6B.

@@

The Barab\'asi-Albert network (7C) presents also a symmetric unimodal
distribution with values higher (on average) than those of the Erd\"{o}s-R\'enyi
random network, this may be the effect of increased communication due to more
efficient network navigability. Interestingly, the network corresponding to the
real FOSISS collaborations (7D) is an asymmetric unimodal distribution in which
moderate to high values of strength of interactions are more likely. We 
hypothesize that this effect is also due to the communication properties of the
network.

@@

An interesting feature of highly communicated networks (characterized by high values of clustering coefficient) is the
fact that certainty among players seems to be enhanced, that is, in such networks the rate of change of strategy is
significantly lower (and smoother) than in poorly connected networks. This is another instance in which easier
communication (i.e. lower average minimum path lengths) lead to better performance of the whole collaborative research
system.\\

@@

{\color{red}Under the assumptions given by the model, we were able to notice
  that, in general, communication within the social
collaborative networks has a positive correlation with average strength of interactions between the individuals partaking in the games and
also with the global collective utility (given by the sum of the individual payoffs). The better the
communication among players, the higher the strength of interactions and the utility leading to an optimized functioning of the whole
\emph{scientific collaboration system}. This is an important result that may be useful for scientific policy planning
and may set a foundation for the optimal use of social networks in scientific collaboration as a means to improve the
relationships among collaborating peers and thus ultimately the performance of research systems. 
We obviously need more qualitative work in order to validate these results from a sociological and anthropological
perspective.\\ %Furthermore, such validation is necessary because, as we said at
             %the beginning of this work, \emph{strength of interactions} can
             %have many different meanings and implementations in the real
             %world. The same we can say about \emph{utility} and most of all,
             %about the very idea of the game we explored here since ``playing
             %the game'' must have so, many different meanings among resarchers
             %and their communities.}\\

{\color{red}To close this article, we would like to comment on three issues we consider important. The first one is about
confronting our results with data available to us from the biomedical research community. Second, some remarks we believe are important
about the role of computational simulations in the social sciences. Finally we would like to comment on our
future work.}\\

@@

{\color{red}FOSISS network is higly hierarchical according to its heterogeneity of $0.873$. Because of it, one would
  expect to find the presence of important hubs \cite{Wu-etal2008}, that is, a few researchers control the whole
  network, as has been reported in some other places \cite{yousefi-etal2008}. Surprisingly, FOSISS network
  centralization is very low $0.023$, i.e. there are no researchers that centralize the majority of connections. Our
  guess is that the network is composed of many small communities or groups with a central researcher or Principal
  Investigator (PI). If this is the case in the FOSISS network, it means that those groups have a very hierarchic structure as well.}\\

{\color{red}Under such structure, when the clustering coefficient is considered, it can be said that groups are also well connected
but that inter-group connections are sparse. In other words, individual groups are strongly connected but the network
as a whole is supported by a small number of links. We came by this idea partially from
another study about scientific collaborations based on co-authorships in one of
the research centers that is part 
of the FOSISS network \cite{HernandezLemus2013}. In the cited reference an apparently well integrated community was
found (high clustering coefficient and a very short characteristic path length). Such integration was mostly
superficial, since it depended on the presence of external collaborators from other research institutions (most of them from overseas). 
Removing these external collaborators broke down the network into small subgraphs that worked independently. Remarkably those subgraphs corresponded to the real
groups of that research center.  What is more, several groups had a hierarchical structure as 
the one we suspect is common in FOSISS subgraphs. The results showed that collaboration was poor between groups but strong
among the members of each group, and that collaboration among groups doesn't emerge bottom-up, instead it seems to be promoted from the
top, from the administrative authorities.}\\

{\color{red}We believe that the the situation just refered is also true for the whole biomedical research community in M\'exico. The
amount of PIs who have also been collaborators in other projects is about one fifth of the total number of participants.
This is a number big enough to connect the whole network in one giant component. Yet, due to the topological
characteristics of the FOSISS network, it appears to be the case that researchers can be the leaders in one project and
collaborators of different project of \emph{its own research group}. CONACyT's funding policies makes it impossible for a
researcher to get a grant from a fund if that researcher has an ongoing project with a grant from that same fund. That
is, a researcher can ask for a grant from FOSISS if and only if at the moment he
doesn't have a grant from FOSISS already. This
policy has lead researchers from the same group to ask for grants from the same fund in order to rise their
budgets. A consequence of this behavior is that group interactions get reinforced, but integroup connections not necessarily so.}\\

{\color{red}As is common among scientific communities in biomedical research, PIs play a central role in the network. Strong PIs and
well connected groups seem to be somehow responsible for the high levels of strength of interactions and the centralization of utility in
our simulation. As for what seems to be phase transitions, in the case of FOSISS networks, these are smoother than
those in the other networks with different topologies, even for those with a small-world topology. We think that this
behavior is also the result of the hierarchical structure already mentioned. If this is true, strength of interactions is first lost in the
edges that link diffrent goups and then in the edges that connect members of the groups. Connections between groups would not
be as dense as those inside the groups, which means that there would not be enough information of the behavior of one group regarding
its neighbors to constrain them as it seems to happen with individual researchers inside their communities. Nevertheless,
if values of the carrying capacity $\nu$ keep increasing and it becomes more
difficult to strengthen interactions, then strength of interactions begins to diminish inside groups.}\\

{\color{red}Another issue that we would like to mention about FOSISS network topology is that it is not a robust collaboration network.
At the level of groups, these might be well connected and consolidated but at the level of the network, this could be
no more than an aggregate of individual groups. A robust network would be resistant to changes in the connections
between groups but in the case of FOSISS, it seems that the network would brake down into
small research groups by cutting some edges, as it happened in our co-authorship
collaboration network \cite{HernandezLemus2013}. The lack of robustness might be 
indicative of the fact that resources stay inside the groups, that is, they do not circulate through or articulate different communities. For
example, one may think of certain expensive technologies for genomic research that could be bought once and shared
among research groups, however, this doesn't seem to happen very often. There are some other
consequences, such as low communication among groups, atomization of practices and know-hows, redundancy in equipment tenancy,
difficulties for implementing community-wide infrastructures such as biobanks, etc.}\\

@@

{\color{red}On these grounds, part of our future work is based on some of the results presented here. We would like to
identify researchers in our simulations and corroborate their situation in the model and in the real world. We are
also interested in going back to the field and interviewing those groups with an interesting behavior found in our
simulations, probably we would follow a similar strategy as the one developed in \cite{Haraetal2003}. Finding
communities beyond the level of the groups is an important task. We think that there are many possibilities that emerge
from the integration of different methodologies. Moreover, studying social processes in science is particularly
attractive due to the amounts of data already available that can be easily collected. This is a privilege because
simulations can be designed on real world data, something that only very recently has become possible
\cite{Barabasi2011}.\\

No doubt, social sciences are getting more ``computational''. This can be seen everywhere, but curiously enough,
disciplines like physicis and computer science are the ones who are moving towards the social sciences and not so much
the other way around. It might be the case that the pioneering disciplines in the computational social sciences will set
the agenda, an agenda that will apparently be mostly based on taking advantage of big data and on hypothesis-free approaches. We
believe that the social sciences have important questions that should be added to that agenda and those questions may not
be answered only by big data techniques but they may require creating models and simulations in the style of the best
hypothesis-driven research.}

@@

\section{acknowledgements}
The authors gratefully acknowledge support by grants: CB-222220-R/2013 and
CB-179431/2012 (Consejo Nacional de Ciencia y Tecnolog\'ia). We would also like
to acknowledge CONACyT for letting us access their database. Finally, we
acknowledge the help of Francisco Allende for his work curating 
databases of researchers.
